Tor's Usability for Censorship Circumvention

### 2015-10-09 paper/circumvention-experiment.tex
added a new section about the configuration interface and a section on the exit survey

@@

\noindent {\bfseries Improved and Alternative Interfaces} We have yet to design the 
improvements to the interface, as they will be based on the data collected from 
the user studies on the current configuration interface. In general, we will measure the 
time it took to configure correctly, and help users avoid common mistakes. An alternate 
interface to automate the configuration process for the user has been proposed in the 
community. One concern about it is that the automation makes the connection process less transparent, 
and since there are countries who log internet activity, automated attempts to obviously
use the Tor network could have the potential to be incriminating.

>>>>

\section{The Configuration Interface}

\noindent {\bfseries Hypotheses} {\color {red} how we came up with these hypotheses, how we will measure these hypotheses, etc.}

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the enviornments require a proxy)
\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e. meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.  
\item {\bfseries H6}: (some dialogue is redundant. see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.  
\end{itemize}

@@

\noindent {\bfseries Improved and Alternative Interfaces} We have yet to design the 
improvements to the interface, as they will be based on the data collected from 
the user studies on the current configuration interface. In general, we will measure the 
time it took to configure correctly, and help users avoid common mistakes. An alternate 
interface to automate the configuration process for the user has been proposed in the 
community. One concern about it is that the automation makes the connection process less transparent, 
and since there are countries who log Internet activity, automated attempts to obviously
use the Tor network could have the potential to be incriminating.\\

\noindent {\bfseries Exit Survey}
{\color {red} talk about the survey here.}
